Verifying Demonstrations

### 2017-11-15 contents-poster.tex
Adds our approach

    \begin{greenblock}{Our approach}
      \dots
    \end{greenblock}

>>>>

    \begin{greenblock}{Our approach}
      \begin{itemize}
        \item The organizer publishes the protest's manifesto (e.g.\ QR-code on 
          placard).
        \item Each protester scans the QR code, computes a protest (cause) 
          identifier (\(cid\)).
        \item Each protester computes a personal identifier (\(pid\)), 
          unlinkable between protests,
        \item Each protester acts as witness (unlinkable between protesters) for 
          other protesters by creating participation-proof shares.
        \item Proof shares are committed to a blockchain.
        \item Anyone can verify the proofs (all shares) and count them.
      \end{itemize}
    \end{greenblock}
